Multisensor Architecture for an Intersection Management System

### 2018-02-21 ch3-arch_sys.tex
Updated communication scheme and data model

For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data. For example a channel containing raw data from a laser scanner could be labeled as "".
%\/sensors\/range\/laser_N\/data\/raw
Redis is also used as in-memory storage for configuration data, which is not dynamic as the date from the processing flow.

@@

The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself. For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.

>>>>

For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data. For example a channel containing raw data from a laser scanner could be labeled as "/sensors/range/laser\_N/data/raw".

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a JSON file and it is available for any client requiring it.

@@

The data model proposed for the system includes the abstraction of the sensing elements, the intersection model and the data used and generated by the processing blocks. For the sensing elements, a Sensor base class and two derived classes, Laser class and Camera class, are defined.

---TODO: Describe and add UML of classes --
-- describe intersection model
--Describe data from flow
